\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}

### 2018-07-07 docs/Manuscript.tex
Added final version ready for submission

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region in the Western Atlantic}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{natbib}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{float}
\floatplacement{figure}{H}

@@

\textsuperscript{1} Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, California,
United States

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the western Atlantic and Caribbean Sea, likely introduced through
liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
the first invasive marine vertebrates established along the North
Atlantic Caribbean coasts
\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
has been labeled as a major marine invasion because they threaten local
biodiversity, spread rapidly, and are difficult to manage
\citep{hixon_2016}.

A substantial amount of research describes lionfish impacts throughout
its invaded range.For example, field experiments by \citet{albins_2008}
showed that lionfish establishment led to reduced recruitment of native
fishes by nearly 80\% over a five week period in Florida.
\citet{green_2012} reported that prey fish biomass declined by 65\% over
two years as lionfish biomass increased along Bahamian coral reefs. A
meta-analysis by \citet{peake_2018} showed that invasive lionfish prey
on at least 167 different species across the tropical and temperate
North Atlantic. Lionfish have also established invasive populations in
other habitats such as estuaries, mangroves, hard-bottomed areas, and
mesophotic reefs
\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017}.
Their feeding behavior and high consumption rates can reduce recruitment
and population sizes of native reef-fish species, and can further
endanger reef fish (\citet{green_2012,rocha_2015}; but see
\citet{hackerott_2017}). These trophic impacts can be minimized if local
lionfish biomass is controlled by culling \citep{ariasgonzalez_2011}.

@@

The feasibility of establishing fisheries through lionfish removal
programs has been extensively evaluated through field observations and
empirical modeling
\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
Determining the feasibility of such initiatives requires modeling the
change in biomass in response to changes in mortality (\emph{i.e.}
culling). A common way to model this is via length-structured population
models, where fish lengths are converted to weight to calculate total
biomass \citep{barbour_2011,cote_2014,andradibrown_2017}. The allometric
length-weight relationship is thus an essential component of these
models, but this relationship can vary across regions as a response to
biotic and abiotic conditions \citep{johnson_2016}.

@@

Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
allometric parameter. Transforming this equation via base-10 logarithms:

@@

Some of the reviewed studies inconsistently defined \(a\) as either the
ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
parameters as mm-to-g conversions when they were in fact cm-to-g
conversions. We standardized each study by converting coefficients and
report all parameters as TL(mm) to TW (gr) conversions. Locations where
allometric studies have been performed are shown in Figure \ref{fig:map}
and Table \ref{tab:all_params}.

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. We used the central Mexican Caribbean as a case study
of how the use of \emph{ex situ} parameters influences the accuracy of
weight estimates for lionfish. We estimated TW from the TL observations
we collected in the central Mexican Caribbean (n = 109) using each of
the 18 parameter pairs and divided predicted weights by known observed
weights to obtain a simple measure of over- or underestimation.
Difference in mean weight ratios across the different parameter pairs
were tested with a one-way analysis of variance (ANOVA) and Tukey's test
was used for post-hoc tests. All analyses were performed in R version
3.5.0 \citep{rcore_2018}. Raw data and code used in this work are
available at dryad.org.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in the coefficient values
\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
\(p < 0.001\)). The allometric factor (\(b\)) was significantly
different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
lionfish present allometric growth. The length-weight coefficients
estimated in this study were within the range identified by studies in
other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
shows the relationship between TL and TW for this region, and model fit
statistics is presented in Table \ref{tab:reg_table}.

There were significant differences in our predicted weights for the
central Mexican Caribbean when using the different pairs of parameters
(\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight estimates
resulted from using the allometric parameters from Banco Chinchorro in
the Caribbean, with mean \(\pm\) SD of 40.37 \(\pm\) 58.74 gr
\citep{sabidoitz_2016}, and the highest weight estimates came from the
Northern Atlantic 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To put
this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
These correspond to predicted-to-observed weights ratios of 0.80 \(\pm\)
0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.

The calculated ratio of predicted-to-observed weight ranged from 0.36 to
3.51, indicating that \emph{ex situ} parameters can result in major
under- and overestimations. Tukey's post-hoc test suggests that weight
ratios for the central Mexican Caribbean were not different from those
obtained with parameters from Little Cayman, the Bahamas, and some sites
in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates using
parameters from the Gulf of Mexico and North-Western Atlantic were
higher on average than those from the Caribbean (Fig
\ref{fig:all_allo}). The average (\(\pm\) SD) predicted-to-observed
weight ratios from these three regions were 1.24 \(\pm\) 0.309, 1.76
\(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
Predicted-to-observed weight ratios are presented in Figure
\ref{fig:bio_ratio}. Spineless weight parameters from \citet{fogg_2013}
still produced predicted-to-observed weight ratios \textgreater{} 1.

@@

The results presented here have major implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in up to a threefold overestimation of TW. These
spatially-driven differences become especially important when allocating
resources for lionfish removal programs, incentivizing lionfish
fisheries as a source of alternative livelihoods, or estimating
ecosystem impacts. Research efforts focused on invasive lionfish
populations need to use parameters calculated for their region to the
extent possible, or at least use reasonable sets of different parameters
that provide upper and lower bounds in their results.

@@

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-10-1.pdf}
\caption{\label{fig:unnamed-chunk-10}\label{fig:l-w-carib}Length-weight
relationship for 109 lionfish sampled in the central Mexican Caribbean.
Points indicate samples, dashed black line indicates curve of best fit,
marginal plots represent the density distribution of each variable.}
\end{figure}

@@

\caption{\label{tab:unnamed-chunk-11}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq. 1 (presented in $\times 10^{-5}$), c = y-intercept for Eq. 3, b = exponent or slope for Eq. 1 or Eq. 3, respectively. The $R^2$ column indicates reported model fit.}
\centering
\begin{tabular}[t]{llllrrll}
\toprule
Region & Sex & n & a & b & c & \$R\textasciicircum{}2\$ & Reference\\
\midrule
Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
\addlinespace
Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
\addlinespace
GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
\addlinespace
GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
\bottomrule
\end{tabular}
\end{table}

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\hypersetup{unicode=true,
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\setlength{\droptitle}{-2em}
  \title{\LARGE{Allometric growth of invasive lionfish (\textit{Pterois spp}) varies by region}}
  \pretitle{\vspace{\droptitle}\centering\huge}
  \posttitle{\par}
  \author{}
  \preauthor{}\postauthor{}
  \date{}
  \predate{}\postdate{}

\usepackage{natbib}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{float}
\floatplacement{figure}{H}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\rhead{Lionfish allometric growth}
\cfoot{\thepage}

@@

\textsuperscript{1} Bren School of Environmental Science and Management,
University of California Santa Barbara, Santa Barbara, California,
United States, 93117

\begin{abstract}
Lionfish (\textit{Pterois volitans / miles}) are an invasive species in the Western Atlantic and the Caribbean. Improving management of invasive lionfish populations requires accurate total biomass estimates, which depend on accurate estimates of allometric growth. Sedentary species like lionfish often exhibit high levels of spatial variation in life history characterstics. We review 17 published length-weight relationships for lionfish taken throughout their invasive range and found substantial regional differences in allometric growth parameters. The spatial pattern we observed is consistent with findings from other studies focusing on genetics or age-at-length. We show that the use of \textit{ex situ} parameters can result in up to a threefold overestimation of total weight, but using parameters from nearby regions reduces this error. These findings can have major implications for management in terms of predicting effects on local ecosystems, evaluating the effectiveness of removal programs, or estimating biomass available for harvest.
\end{abstract}

\textbf{Keywords:} Lionfish, invasive species, length-weight,
allometric, regional variations

@@

Lionfish (\emph{Pterois volitans/miles} complex) are an invasive species
in the western Atlantic and Caribbean Sea, likely introduced through
liberation of aquarium-kept organisms \citep{betancurr_2011}. They are
the first invasive marine vertebrates established along the North
Atlantic Caribbean coasts
\citep{schofield_2009,schofield_2010,sabidoitza_2016} and their presence
has been labeled as a major marine invasion because they threaten local
biodiversity, spread rapidly, and are difficult to manage
\citep{hixon_2016}. Lionfish have established invasive populations in
coral reefs, estuaries, mangroves, hard-bottomed areas, and mesophotic
reefs
\citep{barbour_2010,jud_2011,muoz_2011,claydon_2012,andradibrown_2017,gress_2017}.

A substantial amount of research describes lionfish impacts throughout
its invaded range. A meta-analysis by \citet{peake_2018} showed that
invasive lionfish prey on at least 167 different species across the
tropical and temperate North Atlantic. Their feeding behavior and high
consumption rates can reduce recruitment and population sizes of native
reef-fish species, and can further endanger reef fish
(\citet{green_2012,rocha_2015}; but see \citet{hackerott_2017}). For
example, field experiments by \citet{albins_2008} showed that lionfish
establishment led to reduced recruitment of native fishes by nearly 80\%
over a five week period in Florida. \citet{green_2012} reported that
prey fish biomass declined by 65\% over two years as lionfish biomass
increased along Bahamian coral reefs. Their trophic impacts can be
minimized if local lionfish biomass is controlled by culling
\citep{ariasgonzalez_2011}.

@@

The feasibility of establishing fisheries through lionfish removal
programs has been extensively evaluated through field observations and
empirical modeling
\citep{barbour_2011,morris_2011,deleon_2013,johnston_2015,sandel_2015,usseglio_2017}.
Determining the feasibility of such initiatives requires modeling the
change in biomass in response to changes in fishing mortality
(\emph{i.e.} culling). A common way to model this is via
length-structured population models, where fish lengths are converted to
weight to calculate total biomass
\citep{barbour_2011,cote_2014,andradibrown_2017}. The allometric
length-weight relationship is thus an essential component of these
models, but this relationship can vary across regions as a response to
biotic and abiotic conditions \citep{johnson_2016}.

@@

Where \(a\) is the ponderal index and \(b\) is the scaling exponent or
allometric parameter. Transforming this equation via base-10 logarithms
we obtain:

@@

Some of the reviewed studies inconsistently defined \(a\) as either the
ponderal index from Eq. \ref{eq:allometric} or the y-intercept (\(c\))
from Eq. \ref{eq:log-alo-trans}. Other studies incorrectly reported
parameters as mm-to-g conversions when they were in fact cm-to-g
conversions. We standardized each study by converting coefficients and
report all parameters as TL(mm) to TW (gr) conversions. Locations where
allometric studies have been performed are shown in Figure \ref{fig:map}
and summarized in Table \ref{tab:all_params}.

We obtained a total of 18 parameter pairs by combining length-weight
parameters extracted from the literature and the additional pair
calculated here. We used the central Mexican Caribbean as a case study
of how the use of \emph{ex situ} parameters influences the accuracy of
weight estimates for lionfish. We estimated TW from the TL observations
we collected in the central Mexican Caribbean (n = 109) using each of
the 18 parameter pairs and divided predicted weights by known observed
weights to obtain a simple measure of over- or underestimation.
Difference in mean weight ratios across the different parameter pairs
were tested with a one-way analysis of variance (ANOVA) and Tukey's test
was used for \emph{post-hoc} tests. All analyses were performed in R
version 3.5.0 \citep{rcore_2018}. Raw data and code used in this work
are available on github.

@@

The length-weight relationship for organisms from the central Mexican
Caribbean resulted in the coefficient values
\(a = 3.2056297\times 10^{-6}\), \(b = 3.2347391\) and
\(c = -5.4940866\) (\(R^2 = 0.977\), F(df = 1; 107) = 6928.67,
\(p < 0.001\)). The allometric factor (\(b\)) was significantly
different from \(b = 3\) (\(t(107) = 6.04; p<0.001\)) indicating that
lionfish present allometric growth. The length-weight coefficients
estimated in this study were within the range identified by studies in
other regions (Table \ref{tab:all_params}). Figure \ref{fig:l-w-carib}
shows the relationship between TL and TW for this region, and model fit
statistics are presented in Table \ref{tab:reg_table}.

There were significant differences in our predicted weights for the
central Mexican Caribbean when using the different pairs of parameters
(\(F(df = 17; 1944) = 61.55; p < 0.001\)). The lowest weight estimates
resulted from using the allometric parameters from Banco Chinchorro in
the Caribbean, with mean \(\pm\) SD of 40.37 \(\pm\) 58.74 gr
\citep{sabidoitz_2016}, and the highest weight estimates came from the
Northern Atlantic with 73.76 \(\pm\) 96.11 gr \citep{barbour_2011}. To
put this in context, true observed weights were 52.56 \(\pm\) 76.58 gr.
These correspond to predicted-to-observed weights ratios of 0.80 \(\pm\)
0.19 and 1.76 \(\pm\) 0.50 (mean \(\pm\) SD), respectively.

The calculated ratio of predicted-to-observed weight ranged from 0.36 to
3.51, indicating that \emph{ex situ} parameters can result in major
under- and overestimations. Tukey's \emph{post-hoc} test suggests that
weight ratios for the central Mexican Caribbean were not different from
those obtained with parameters from Little Cayman, the Bahamas, and some
sites in the Gulf of Mexico (Tukeys HSD \(p > 0.05\)). Weight estimates
using parameters from the Gulf of Mexico and North-Western Atlantic were
higher on average than those from the Caribbean (Fig
\ref{fig:all_allo}). The average (\(\pm\) SD) predicted-to-observed
weight ratios from these three regions were 1.24 \(\pm\) 0.309, 1.76
\(\pm\) 0.496, and 1.17 \(\pm\) 0.398, respectively.
Predicted-to-observed weight ratios are presented in Figure
\ref{fig:bio_ratio}. Spineless weight parameters from \citet{fogg_2013}
still produced predicted-to-observed weight ratios \textgreater{} 1.

@@

The results presented here have major implications for management. For
example, \citet{edwards_2014} simulated a lionfish culling program under
two scenarios, one using length-at-age and length-to-weight parameters
from North Carolina and one using parameters from Little Cayman. Their
results show that using different parameters caused up to a four-year
difference in the time required for the simulated lionfish population to
recover to 90\% of its initial biomass after removals ceased. Here, we
show that using one set of length-weight parameters versus another for a
given length can result in more than a threefold overestimation of TW.
These spatially-driven differences become especially important when
allocating resources for lionfish removal programs, incentivizing
lionfish fisheries as a source of alternative livelihoods, or estimating
ecosystem impacts. Research efforts focused on invasive lionfish
populations need to use parameters calculated for their region to the
extent possible, or at least use reasonable sets of different parameters
that provide upper and lower bounds in their results.

@@

\begin{figure}
\centering
\includegraphics{Manuscript_files/figure-latex/unnamed-chunk-9-1.pdf}
\caption{\label{fig:unnamed-chunk-9}\label{fig:l-w-carib}Length-weight
relationship for 109 lionfish sampled in the central Mexican Caribbean.
Points indicate samples, dashed black line indicates curve of best fit,
marginal plots represent the density distribution of each variable.}
\end{figure}

@@

@@

\caption{\label{tab:unnamed-chunk-11}\label{tab:all_params}Summary of 18 allometric growth parameters available for lionfish in the invaded range from peer-reviewed literature and this study. All parameters have been adjusted to convert from millimeters to grams. n = Sample size, Sex specifies whether data was presented for Females (F), Males (M), or both genders combined (B), a = scaling parameter for Eq. 1 (presented in $\times 10^{-5}$), c = y-intercept for Eq. 3, b = exponent or slope for Eq. 1 or Eq. 3, respectively. The Fit column contains the reported $R^2$ of the model fit.}
\centering
\begin{tabular}[t]{llllrrll}
\toprule
Region & Sex & n & a & b & c & Fit & Reference\\
\midrule
Caribbean & B & 458 & 3.6 & 2.81 & -4.44 & - & Sandel et al., 2015\\
Caribbean & B & 419 & 2.8 & 2.85 & -4.56 & 0.8715 & Chin et al., 2016\\
Caribbean & B & 1450 & 2.3 & 2.89 & -4.64 & 0.96 & de Leon et al., 2013\\
Caribbean & B & 1887 & 0.3 & 3.24 & -5.52 & 0.97 & Edwards et al., 2014\\
Caribbean & B & - & 0.25 & 3.29 & -5.60 & - & Darling et al., 2011\\
\addlinespace
Caribbean & B & 2143 & 0.52 & 3.18 & -5.28 & 0.9907 & Sabido-Itza et al., 2016\\
Caribbean & B & 227 & 0.8 & 3.11 & -5.10 & 0.958 & Toledo-Hernández et al., 2014\\
Caribbean & B & 449 & 0.23 & 3.25 & -5.64 & 0.97 & Sabido-Itza et al., 2016b\\
Caribbean & B & 368 & 0.32 & 3.19 & -5.50 & 0.98 & Sabido-Itza et al., 2016b\\
Caribbean & B & 109 & 0.32 & 3.23 & -5.49 & 0.9766 & This study\\
\addlinespace
GoM & B & 934 & 0.21 & 3.34 & -5.68 & 0.98 & Dahl \& Patterson, 2014\\
GoM & B & 472 & 0.29 & 3.30 & -5.54 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & F & 67 & 0.12 & 3.47 & -5.93 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & M & 59 & 0.42 & 3.23 & -5.38 & 0.95 & Aguilar-Perera \& Quijano-Puerto, 2016\\
GoM & B & 582 & 0.14 & 3.43 & -5.86 & 0.99 & Fogg et al., 2013\\
\addlinespace
GoM & M & 119 & 0.27 & 3.31 & -5.57 & 0.97 & Fogg et al., 2013\\
GoM & F & 115 & 0.68 & 3.14 & -5.17 & 0.94 & Fogg et al., 2013\\
North Atlantic & B & 774 & 2.9 & 2.89 & -4.54 & - & Barbour et al., 2011\\
\bottomrule
\end{tabular}
\end{table}
